Second-Generation Web Interface to Correcting ASR Output

### 2018-05-22 2018-ftc-vancouver/webapp.tex
fine tuning for FTC 2018

Mako\v{n}'s written works present his teachings in a systematic, comprehensible
fashion, while the recordings offer bonuses: talks tailored to the audience,
answers to questions, personal experiences, behind-the-scenes to the books etc.
The archive is freely accessible under the CC-BY license.

@@

@@

Our project is not the first involving community-driven corpus annotation. We
can mention the Manually annotated sub-corpus\cite{ide2010manually}, where
annotations of various kinds are gathered from volunteers, or the
Wikicorpus\cite{reese2010wikicorpus}, a corpus of Wikipedia articles with some
linguistic annotation. Our project may reach profound similarities with these in
the future, when we no longer focus on the transcription itself but rather on
annotation. There is also CzEng\cite{bojar2008czeng}, the Czech-English Parallel
Corpus, where a large part of the translation is provided by volunteers. The
similarity in setting is considerable as both projects involve a
machine-produced erroneous derivative of the original material (in our case
audio transcriptions, in the case of CzEng Czech translations of English texts),
and a community of volunteers correct these. But the specifics of the projects
bring different challenges and dictate different approaches. Marge
(2009)\cite{5494979} investigates using The Mechanical Turk to obtain audio
transcriptions. Mihalcea (2004)\cite{mihalcea2004building} offers a web
interface for word-sense disambiguation but focuses mostly on annotator conflict
resolution.

@@

We have no special assumption of the user beyond basic computer usage skills and
understanding the audio. We assume no prior training. There is a manual for
clearing common points of confusion. The main message in it is that anything
that is to be transcribed, should be should be transcribed with respect to
phonetic precision, even if it results in nonsensical character strings.

Anything except words spoken by the one speaker of interest is to be left
untranscribed, including noise or speech by other persons\footnote{We may later
add a speaker annotation}. Incomprehensible words are to be left uncorrected
(the ASR output kept) if the phones are unclear. If the phones uttered are clear
but it is not clear what word was meant, the word may be transcribed
phonetically.

A submitted transcribed segment always overwrites the present version but we
keep all the submissions in a database, so undo operations, clustering
submissions by their author etc. are possible but we had little need for this so
far.

@@

We shall only discuss the detail view as the others are not relevant to this
article. Figure~\ref{fig:scn1lab} shows the interface during playback.
Figure~\ref{fig:scn2lab} shows the interface while a segment is being edited.
The interface in the figures is conveniently shown in English, although in
reality it is in Czech.

@@

\begin{figure}[htpb]
\includegraphics[scale=0.6]{rc/radio-makon-en-2-lab.png}
\caption{Interface in the state of editing a segment, with labels}
\label{fig:scn2lab}
\end{figure}

@@

Most common tasks have keyboard shortcuts: \texttt{ctrl+space} for play/pause
and \texttt{ctrl+enter} for submitting a correction.

@@

One of the features that Transcribe, the only commercial tool in our reference
list, offers is setting up keyboard shortcuts for common words. We have not
implemented this because ideally, common words should be covered by the speech
recognition. However, it could be sensible to implement it anyway. The reason is
that a word can be very rare globally and thus poorly recognized by ASR but very
common in a specific passage. This particularly regards named entities.

@@

Apart from this, the version of the transcription to the recording is updated.
This is because the transcriptions have a long cache time because normally, they
do not change at all. At the page load, the versions of all transcriptions are
loaded and used as cache busters. This enables us to use an external CDN and
cache effectively.

@@

Among the states the app can enter is simple playback, inspecting a word and
transcribing a segment. Now, the only relevant things we actually keep in the
Redux store are:

@@

>>>>

Mako\v{n}'s written works present his teachings in a systematic, comprehensible
fashion, while the recordings offer bonuses: talks tailored to the audience,
answers to questions, personal experiences, behind-the-scenes to the books etc.
The archive is freely
accessible\footnote{https://lindat.mff.cuni.cz/repository/xmlui/handle/11372/LRT-1455}
under the CC-BY license.

@@

With regard to the transription as presented to the user, a submitted segment of
transcription always overwrites the present version but we keep all the
submissions in a database, so undo operations, clustering submissions by their
author etc. are possible but we had little need for this so far.

@@

Our project is not the first involving community-driven care of a corpus. We
can mention the Manually annotated sub-corpus\cite{ide2010manually}, where
annotations of various kinds are gathered from volunteers, or the
Wikicorpus\cite{reese2010wikicorpus}, a corpus of Wikipedia articles with some
linguistic annotation. Our project may reach profound similarities with these in
the future, when we no longer focus on the transcription itself but rather on
annotation.

There is also CzEng\cite{bojar2008czeng}, the Czech-English Parallel
Corpus, where a large part of the translation is provided by volunteers. The
similarity in setting is considerable as both projects involve a
machine-produced erroneous derivative of the original material (in our case
audio transcriptions, in the case of CzEng Czech translations of English texts),
and a community of volunteers correct these. But the specifics of the projects
bring different challenges and dictate different approaches.

Marge (2009)\cite{5494979} investigates using The Mechanical Turk to obtain
audio transcriptions. Mihalcea (2004)\cite{mihalcea2004building} offers a web
interface for word-sense disambiguation and focuses mostly on annotator conflict
resolution.

@@

We have no special assumption of the user beyond basic computer usage skills and
understanding the audio. We assume no prior training. There is a manual for
clearing common points of confusion. The main message in it is that anything
that is to be transcribed, should be transcribed with respect to
phonetic precision, even if it results in nonsensical character strings.

Anything except words spoken by the one speaker of interest is to be left
untranscribed, including noise or speech by other persons\footnote{In our data,
other speakers represent a negligible fraction but we may later add support for
speaker annotation.}. Incomprehensible words are to be left uncorrected
(the ASR output kept) if the phones are unclear. If the phones uttered are clear
but it is not clear what word was meant, the word may be transcribed
phonetically.

@@

We shall only discuss the detail view as the others are not relevant to this
paper. Figure~\ref{fig:scn1lab} shows the interface during playback.
Figure~\ref{fig:scn2lab} shows the interface while a segment is being edited.
The interface in the figures is conveniently shown in English, although in
reality it is in Czech.

@@

\begin{figure}[htpb]
\includegraphics[scale=0.6]{rc/radio-makon-en-2-lab.png}
\caption{Interface in the state of editing a segment}
\label{fig:scn2lab}
\end{figure}

@@

The most common tasks have keyboard shortcuts: \texttt{ctrl+space} for
play/pause and \texttt{ctrl+enter} for submitting a correction.

@@

One of the features that Transcribe, the only commercial tool in our reference
list, offers is setting up keyboard shortcuts for common words. We have not
implemented this because ideally, common words should be covered by speech
recognition. However, it could be sensible to implement it anyway. The reason is
that a word can be very rare globally and thus poorly recognized by ASR but very
common in a specific passage. This particularly regards named entities.

@@

Apart from this, the version of the transcription to the recording is updated.
This is because the transcription files have a long cache time because normally,
they do not change at all. At the page load, the versions of all transcriptions
are loaded and used as cache busters. This enables us to use an external CDN and
cache effectively.

@@

Among the states the app can enter is simple playback, inspecting a word and
transcribing a segment. The only relevant things we actually keep in the
Redux store are:

@@

We shall also deploy the technology on a different data set once we find a good
fit.
